True versus apparent shapes of bow shocks

### 2017-12-05 papers/Paper1/quadrics-bowshock.tex
Add a new appendix on the circle fits
Add acknowledgements and email addresses

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango Yong \& Henney]{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}

@@

\input{sec-intro}
% \input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-thin-shell}
% \input{app-dust-wave}
% \input{sec-standing-wave}
\input{sec-conclusions}
\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}
\appendix
\input{app-parabola}
%\input{app-ancantoid}
\input{app-shape-parameters}
% \input{app-dust-equations}

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

>>>>

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango Yong \& Henney]{
  Jorge A. Tarango Yong\thanks{E-mail: j.tarango@irya.unam.mx}
  \& William J. Henney\thanks{E-mail: w.henney@irya.unam.mx}\\
  \AddressCRyA
}

@@

\input{sec-intro}
% \input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-thin-shell}
% \input{app-dust-wave}
% \input{sec-standing-wave}
\input{sec-conclusions}

\section*{Acknowledgements}

We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grant Programa de Apoyo a Proyectos de Investigación e
Inovación Tecnológica IN111215.  JATY acknowledges support via a
research studentship from Consejo Nacional de Ciencias y Tecnología,
Mexico.

\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}
\appendix
\input{app-parabola}
%\input{app-ancantoid}
\input{app-shape-parameters}
% \input{app-dust-equations}
\input{app-rcurv-empirical}
% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

### 2017-12-05 papers/Paper1/sec-conclusions.tex
Add acknowledgements and email addresses

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-r0-prime}
  \caption[]{Apparent projected apex distance of simulations.  Line
    and symbol meanings are as in Figure~\ref{fig:sim-Pi-Lambda}.  In
    addition, triangle symbols at \(\abs{i} = \ang{0}\) denote radius
    measured on H\(\alpha\) optical emission maps.  Note that the distances
    for the blue square symbols have been adjusted for the correction
    factor discussed in footnote~\ref{fn:meyer-correction}.}
  \label{fig:sim-R0-prime}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-r0-prime}
  \caption[]{Apparent projected apex distance of simulations.  Line
    and symbol meanings are as in Figure~\ref{fig:sim-Pi-Lambda}.  In
    addition, triangle symbols at \(\abs{i} = \ang{0}\) denote radius
    measured on H\(\alpha\) optical emission maps.  Note that the distances
    for the blue square symbols have been adjusted according to the
    correction factor discussed in
    footnote~\ref{fn:meyer-correction}.}
  \label{fig:sim-R0-prime}
\end{figure}
